Covid-19 infection and attributable mortality in residents of UK care homes: Cohort study using electronic records (March-June 2020)

### 2020-07-12 manuscript/manuscript.Rmd
minor fixes

```{r tablefiller1, results="asis"}
arsenal::tableby(
  confirmed  ~ gender + ageg  +  home_type + user_type2  + staff_to_bed_ratio_g5 +  occ_bedroom_ratio_g6, 
  control = arsenal::tableby.control(test = FALSE, cat.stats = "countrowpct", digits = 1L),
  data = residents_overview) %>%  summary()

@@

```{r tablefiller2, results="asis"}
residents_overview$death_status <- as.integer(residents_overview$status == "Deceased")
arsenal::tableby(
  death_status  ~ gender + ageg  +  home_type + user_type2  + staff_to_bed_ratio_g5 +  occ_bedroom_ratio_g6, 
  control = arsenal::tableby.control(test = FALSE, cat.stats = "countrowpct", digits = 1L),
  data = residents_overview) %>%  summary()

@@

### Attributable mortality

@@

#The unique surveillance system we established in partnership with FSHCG allowed us to track infections throughout the entire pandemic period across a large number of care homes, and identify symptomatic as well as confirmed and asymptomatic cases. To our knowledge, this is the most compete reporting system for Covid-19 infections in care homes published to date.  It is possible that care homes that paid less attention to active surveillance to support control will have had higher levels of uncontrolled outbreaks compared to those seen in this study.

@@

| Residents     |  Symptomatic  |  Confirmed  | All-cause death | 
| ------------- | -------------:| -------------:|-------------:|
| Cases      | `r formatbm(desc_residents$DAT_total_symptomatic)` |	`r formatbm(desc_residents$unique_residents_test_result_positive)` | `r formatbm(desc_residents$DAT_total_deaths)`  |
|	$N$ exposed  | `r formatbm(desc_residents$DAT_total_residents)`|	`r formatbm(desc_residents$DAT_total_residents)` | `r formatbm(desc_residents$DAT_total_residents)` |
|	Total exposure (days)|`r formatbm(desc_residents$DAT_total_symptomatic_denom)`|	`r formatbm(desc_residents$DAT_total_confirmed_denom)` | `r formatbm(desc_residents$total_denom)` |
|	Incidence proportion (%)  | `r tbrounding(desc_residents$DAT_p_symptomatic)` [`r tbrounding(desc_residents$DAT_p_symptomatic_lower)`; `r tbrounding(desc_residents$DAT_p_symptomatic_upper)`] |`r tbrounding(desc_residents$DAT_p_confirmed)` [`r tbrounding(desc_residents$DAT_p_confirmed_lower)`; `r tbrounding(desc_residents$DAT_p_confirmed_upper)`] |`r tbrounding(desc_residents$DAT_p_death)` [`r tbrounding(desc_residents$DAT_p_death_lower)`; `r tbrounding(desc_residents$DAT_p_death_upper)`] |
|	Incidence rate (per 100,000) | `r tbrounding(desc_residents$DAT_IR_symptomatic)` [`r tbrounding(desc_residents$DAT_IR_symptomatic_lower)`; `r tbrounding(desc_residents$DAT_IR_symptomatic_upper)`] | `r tbrounding(desc_residents$DAT_IR_confirmed)`  [`r tbrounding(desc_residents$DAT_IR_confirmed_lower)`; `r tbrounding(desc_residents$DAT_IR_confirmed_upper)`] | `r tbrounding(desc_residents$DAT_IR_death)` [`r tbrounding(desc_residents$DAT_IR_death_lower)`; `r tbrounding(desc_residents$DAT_IR_death_upper)` ]|

>>>>

```{r tablefiller1, results="asis"}
arsenal::tableby(
  confirmed  ~ gender + ageg  +  home_type + user_type2 +bed_tot_category + bed_to_staff_ratio +  occ_bedroom_ratio_g6, 
  control = arsenal::tableby.control(test = FALSE, cat.stats = "countrowpct", digits = 1L),
  data = residents_overview) %>%  summary()

@@

```{r tablefiller2, results="asis"}
residents_overview$death_status <- as.integer(residents_overview$status == "Deceased")
arsenal::tableby(
  death_status  ~ gender + ageg  +  home_type + user_type2  + bed_to_staff_ratio + bed_tot_category +  occ_bedroom_ratio_g6 + covid_status_outbreak, 
  control = arsenal::tableby.control(test = FALSE, cat.stats = "countrowpct", digits = 1L),
  data = residents_overview) %>%  summary()

@@

## Attributable mortality

@@

The unique surveillance system we established in partnership with FSHCG allowed us to track infections throughout the entire pandemic period across a large number of care homes, and identify symptomatic as well as confirmed and asymptomatic cases. To our knowledge, this is the most compete reporting system for Covid-19 infections in care homes published to date.  It is possible that care homes that paid less attention to active surveillance to support control will have had higher levels of uncontrolled outbreaks compared to those seen in this study.

@@

| Residents     |  Symptomatic  |  Confirmed  | All-cause death | 
| ------------- | -------------:| -------------:|-------------:|
| Cases      | `r formatbm(desc_residents$DAT_total_symptomatic)` |	`r formatbm(desc_residents$unique_residents_test_result_positive)` | `r formatbm(desc_residents$DAT_total_deaths)`  |
|	$N$ exposed  | `r formatbm(desc_residents$DAT_total_residents)`|	`r formatbm(desc_residents$DAT_total_residents)` | `r formatbm(desc_residents$DAT_total_residents)` |
|	Total exposure (days)|`r formatbm(desc_residents$DAT_total_symptomatic_denom)`|	`r formatbm(desc_residents$DAT_total_confirmed_denom)` | `r formatbm(desc_residents$total_denom)` |
|	Cumulative incidence (%)  | `r tbrounding(desc_residents$DAT_p_symptomatic)` [`r tbrounding(desc_residents$DAT_p_symptomatic_lower)`; `r tbrounding(desc_residents$DAT_p_symptomatic_upper)`] |`r tbrounding(desc_residents$DAT_p_confirmed)` [`r tbrounding(desc_residents$DAT_p_confirmed_lower)`; `r tbrounding(desc_residents$DAT_p_confirmed_upper)`] |`r tbrounding(desc_residents$DAT_p_death)` [`r tbrounding(desc_residents$DAT_p_death_lower)`; `r tbrounding(desc_residents$DAT_p_death_upper)`] |
|	Incidence rate (per 100,000) | `r tbrounding(desc_residents$DAT_IR_symptomatic)` [`r tbrounding(desc_residents$DAT_IR_symptomatic_lower)`; `r tbrounding(desc_residents$DAT_IR_symptomatic_upper)`] | `r tbrounding(desc_residents$DAT_IR_confirmed)`  [`r tbrounding(desc_residents$DAT_IR_confirmed_lower)`; `r tbrounding(desc_residents$DAT_IR_confirmed_upper)`] | `r tbrounding(desc_residents$DAT_IR_death)` [`r tbrounding(desc_residents$DAT_IR_death_lower)`; `r tbrounding(desc_residents$DAT_IR_death_upper)` ]|
